---
title: "GBC Alpraz: The effects of GABAergic agonists on global brain connectivity"
author: "Valerie Jill Sydnor"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ciftiTools)
ciftiTools.setOption('wb_path', '/Users/valeriesydnor/Software/workbench/')
library(gifti)
library(cifti)
library(ggseg)
library(ggsegExtra)
library(ggsegGlasser)
library(ggsegSchaefer)
library(viridis)
require(ggplot2)
library(ppcor)
library(dplyr)
library(e1071)
library(matrixTests)
library(doParallel)
```

Read in Alpraz Participant Data 
```{r}
participants <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/sub_ses_passQC_finallist.csv", header = FALSE)
```

Read in Atlases  
```{r}
SAaxis.schaefer <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/software/S-A_ArchetypalAxis/Schaefer400_17Network/Sensorimotor_Association_Axis_AverageRanks.csv", header=T)
SAaxis.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/software/S-A_ArchetypalAxis/Glasser360_MMP/Sensorimotor_Association_Axis_AverageRanks.csv", header=T)
brainmaps.schaefer <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/software/S-A_ArchetypalAxis/Schaefer400_17Network/brainmaps_schaefer.csv", header=T)
brainmaps.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/software/S-A_ArchetypalAxis/Glasser360_MMP/brainmaps_glasser.csv", header=T)
schaefer.parcel.labels <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/atlases/schaefer400_regionlist.csv", header = T)
glasser.parcel.labels <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/atlases/glasser360_regionlist.csv", header = T)
mappys <- read.csv("/Users/valeriesydnor/Software/mappys/mappings_400.csv")
mappys$label <- schaefer.parcel.labels$label
```

Read in Cortical Mask
```{r}
schaefer400.parcelmask.thresholded <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/atlases/study_cortexmask_schaefer400_thresholded.txt")
glasser360.parcelmask.threshold <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/atlases/study_cortexmask_glasser360_thresholded.txt")
```

## Compute Global Brain Connectivity (GBC)

```{r}
computeGBC <- function(subid, sesid, atlas, method){
  
  #read in connectivity matrix
  if(atlas == "schaefer"){
    connect.matrix <- read_cifti(sprintf("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/xcpabcd/task_regress/surface/xcp_abcd/%1$s/%2$s/func/%1$s_%2$s_task-emotionid_space-fsLR_atlas-Schaefer417_den-91k_den-91k_bold.pconn.nii", subid, sesid))
    cortical.mask <- schaefer400.parcelmask.thresholded$x
    }
  if(atlas == "glasser"){
    connect.matrix <- read_cifti(sprintf("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/xcpabcd/task_regress/surface/xcp_abcd/%1$s/%2$s/func/%1$s_%2$s_task-emotionid_space-fsLR_atlas-Glasser_den-91k_den-91k_bold.pconn.nii", subid, sesid))
    cortical.mask <- glasser360.parcelmask.threshold$x
    }

  #compute average connectivity 
  if(method == "reg"){
    GBC.unmasked <- as.array(rowMeans(connect.matrix$data, na.rm = T)) #calculate average connectivity, ignoring parcels outside the FOV
    GBC <- sweep(GBC.unmasked, MARGIN = 1, cortical.mask, `*`)
    GBC <- as.data.frame(GBC)
    GBC[GBC == 0] <- NA  
  }
  if(method == "pos"){
    connect.matrix$data <- replace(connect.matrix$data, which(connect.matrix$data < 0), NA)
    GBC.unmasked <- as.array(rowMeans(connect.matrix$data, na.rm = T)) #calculate average connectivity, ignoring parcels outside the FOV
    GBC <- sweep(GBC.unmasked, MARGIN = 1, cortical.mask, `*`)
    GBC <- as.data.frame(GBC)
    GBC[GBC == 0] <- NA  
  }
  if(method == "abs"){
    GBC.unmasked <- as.array(rowMeans(abs(connect.matrix$data), na.rm = T)) #calculate average connectivity, ignoring parcels outside the FOV
    GBC <- sweep(GBC.unmasked, MARGIN = 1, cortical.mask, `*`)
    GBC <- as.data.frame(GBC)
    GBC[GBC == 0] <- NA  
  }
  if(method == "sum"){
    connect.matrix$data <- replace(connect.matrix$data, which(connect.matrix$data >= 0.25), 1)
    connect.matrix$data <- replace(connect.matrix$data, which(connect.matrix$data <= -0.25), 1)
    connect.matrix$data <- replace(connect.matrix$data, which(connect.matrix$data != 1), 0)
    GBC.unmasked <- as.array(rowSums(connect.matrix$data), na.rm = T) #calculate average connectivity, ignoring parcels outside the FOV
    GBC <- sweep(GBC.unmasked, MARGIN = 1, cortical.mask, `*`)
    GBC <- as.data.frame(GBC)
    GBC[GBC == 0] <- NA  
  }
  return(GBC)
  }
```

```{r, echo=T, eval=F, warning=F, message=F}
GBC.subxparcel.matrix.schaefer <- matrix(data = NA, nrow = 84, ncol = 404)
regionheaders <- schaefer.parcel.labels$label
demoheaders <- c("subid","sesid","drug","meanFD")
colheaders <- as.matrix(c(demoheaders,regionheaders))
colnames(GBC.subxparcel.matrix.schaefer) <- colheaders

for(row in c(1:nrow(participants))){
  subid=participants[row,1]
  sesid=participants[row,2]
  drug=participants[row,3]
  meanFD=participants[row,4]
  data <- computeGBC(subid, sesid, "schaefer", "sum")
  df <- cbind(subid, sesid, drug, meanFD, t(data))
  GBC.subxparcel.matrix.schaefer[row,] <- df
}

GBC.subxparcel.matrix.glasser <- matrix(data = NA, nrow = 84, ncol = 364)
regionheaders <- glasser.parcel.labels$orig_parcelname
demoheaders <- c("subid","sesid","drug","meanFD")
colheaders <- as.matrix(c(demoheaders,regionheaders))
colnames(GBC.subxparcel.matrix.glasser) <- colheaders

for(row in c(1:nrow(participants))){
  subid=participants[row,1]
  sesid=participants[row,2]
  drug=participants[row,3]
  meanFD=participants[row,4]
  data <- computeGBC(subid, sesid, "glasser", "sum")
  df <- cbind(subid, sesid, drug, meanFD, t(data))
  GBC.subxparcel.matrix.glasser[row,] <- df
}

write.csv(GBC.subxparcel.matrix.schaefer, "/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/sumGBC_subxparcel_matrix_schaefer.csv", row.names=F, quote=F)
write.csv(GBC.subxparcel.matrix.glasser, "/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/sumGBC_subxparcel_matrix_glasser.csv", row.names=F, quote=F)
```

```{r}
GBC.schaefer <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC_subxparcel_matrix_schaefer.csv")
GBC.glasser <- read.csv("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC_subxparcel_matrix_glasser.csv")
```

## Visualize GBC Map

**Visualze across-cortex regional homogeneity: Schaefer**

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=F}
GBC.schaefer.map <- GBC.schaefer %>% dplyr::select(-subid, -sesid, -drug, -meanFD)
GBC.schaefer.map <- colMeans(GBC.schaefer.map)
GBC.schaefer.map <- as.data.frame(GBC.schaefer.map)
GBC.schaefer.map$label <- schaefer.parcel.labels$label

ggseg(.data = GBC.schaefer.map, atlas = "schaefer17_400", mapping=aes(fill=GBC.schaefer.map), position = c("stacked")) + theme_void() + scale_fill_gradientn(colors = viridis_pal(option="B")(10))
```

**Visualze across-cortex regional homogeneity: Glasser**

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=F}
GBC.glasser.map <- GBC.glasser %>% dplyr::select(-subid, -sesid, -drug, -meanFD)
GBC.glasser.map <- colMeans(GBC.glasser.map)
GBC.glasser.map <- as.data.frame(GBC.glasser.map)
GBC.glasser.map$label <- glasser.parcel.labels$label

ggseg(.data = GBC.glasser.map, atlas = "glasser", mapping=aes(fill=GBC.glasser.map), position = c("stacked")) + theme_void() + scale_fill_gradientn(colors = viridis_pal(option="B")(10))
```

## Relationship to S-A Axis and Inhibitory Interneurons

### S-A Axis

```{r echo=FALSE}
print("Schaefer S-A Axis")
cor.test(GBC.schaefer.map$GBC.schaefer.map, SAaxis.schaefer$finalrank.wholebrain, method=c("spearman"),exact=F)
print("Glasser S-A Axis")
cor.test(GBC.glasser.map$GBC.glasser.map[181:360], SAaxis.glasser$brains.average.rank, method=c("spearman"),exact=F)
```

### T1T2 Hierarchy

```{r echo=FALSE}
print("Schaefer T1T2")
cor.test(GBC.schaefer.map$GBC.schaefer.map, brainmaps.schaefer$T1T2ratio , method=c("spearman"))
print("Glasser T1T2")
cor.test(GBC.glasser.map$GBC.glasser.map[181:360], brainmaps.glasser$T1T2ratio, method=c("spearman"))
```

### Inhibitory Interneurons

* PVALB

```{r echo=FALSE}
cor.test(GBC.schaefer.map$GBC.schaefer.map, mappys$PVALB , method=c("spearman"))
```

* SST

```{r echo=FALSE}
cor.test(GBC.schaefer.map$GBC.schaefer.map, mappys$SST , method=c("spearman"))
```

## Placebo versus GABA Agonist Paired T-tests

### Schaefer

#### P-values

```{r, warning=F, comment=F}
drug <- GBC.schaefer %>% filter(drug == 0)
drug <- drug %>% select(-subid, -sesid, -drug, -meanFD)
placebo <- GBC.schaefer %>% filter(drug == 1)
placebo <- placebo %>% select(-subid, -sesid, -drug, -meanFD)

#run paired t-tests on each parcel (column)
tstats <- col_t_paired(drug, placebo)
```

```{r echo=FALSE}
num <- nrow(as.data.frame(tstats$pvalue) %>% filter(`tstats$pvalue` < 0.05))
print(sprintf("Number of significant parcels (uncorrected): %s", num))
```

#### P-value Histograms 

```{r echo=FALSE}
#p-value histograms
ps.fdr <- p.adjust(na.omit(tstats$pvalue))
par(mfrow=c(1,2))
hist(tstats$pvalue, col = "#781d75", xlab = "Paired t-test p-values", main="")
hist(ps.fdr, col = "#c76612", xlab = "Paired t-test FDR-corrected p-values", main="")
```

#### T-statistic Histogram

```{r echo=FALSE}
#distribution of t-values
hist(tstats$statistic, col = "#e8b323", xlab = "Paired t-test t-values", main="")
```

#### T-statistic Map

*GBC higher in GABA > placebo, the t-statistic is positive (yellow)  

*GBC lower in GABA < placebo, the t-statistic is negative (purple)

```{r, warning=F, echo=F, comment=F, message=F}
tstatistics <- tstats$statistic
tstatistics <- as.data.frame(tstatistics)
tstatistics$label <- schaefer.parcel.labels$label

ggseg(.data = tstatistics, atlas = "schaefer17_400",  mapping=aes(fill=tstatistics), position = c("stacked")) + theme_void() + scale_fill_gradient2(high= "goldenrod1", mid = "white", low = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL)
```

### Glasser

#### P-values

```{r, warning=F, comment=F}
drug <- GBC.glasser %>% filter(drug == 0)
drug <- drug %>% select(-subid, -sesid, -drug, -meanFD)
placebo <- GBC.glasser %>% filter(drug == 1)
placebo <- placebo %>% select(-subid, -sesid, -drug, -meanFD)

#run paired t-tests on each parcel (column)
tstats <- col_t_paired(drug, placebo)
```

```{r echo=FALSE}
num <- nrow(as.data.frame(tstats$pvalue) %>% filter(`tstats$pvalue` < 0.05))
print(sprintf("Number of significant parcels (uncorrected): %s", num))
```

#### P-value Histograms 

```{r echo=FALSE}
#p-value histograms
ps.fdr <- p.adjust(na.omit(tstats$pvalue))
par(mfrow=c(1,2))
hist(tstats$pvalue, col = "#781d75", xlab = "Paired t-test p-values", main="")
hist(ps.fdr, col = "#c76612", xlab = "Paired t-test FDR-corrected p-values", main="")
```

#### T-statistic Histogram

```{r echo=FALSE}
#distribution of t-values
hist(tstats$statistic, col = "#ffd000", xlab = "Paired t-test t-values", main="")
```

#### T-statistic Map

*GBC higher in GABA > placebo, the t-statistic is positive (yellow)  

*GBC lower in GABA < placebo, the t-statistic is negative (purple)

```{r, warning=F, echo=F, comment=F, message=F}
tstatistics <- tstats$statistic
tstatistics <- as.data.frame(tstatistics)
tstatistics$label <- glasser.parcel.labels$label

ggseg(.data = tstatistics, atlas = "glasser",  mapping=aes(fill=tstatistics), position = c("stacked")) + theme_void() + scale_fill_gradient2(high= "goldenrod1", mid = "white", low = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL)
```

## PCA and Logistic Regression

### Schaefer

#### PCA Variance Explained

```{r}
inputmatrix <- GBC.schaefer
inputmatrix <- inputmatrix %>% dplyr::select(-subid, -sesid, -drug, -meanFD) 
inputmatrix <- inputmatrix %>% mutate_if(is.character,as.numeric)
inputmatrix <- as.data.frame(inputmatrix) #convert matrix to df
inputmatrix[inputmatrix == 0] <- NA
inputmatrix.cleaned <- inputmatrix[, unlist(lapply(inputmatrix, function(x) !all(is.na(x))))] #remove all columns (parcels) with null data (all NAs) #84x232
GBC.pca.schaefer <- prcomp(inputmatrix.cleaned, scale. = TRUE, center = TRUE) 
print(summary(GBC.pca.schaefer)$importance[2,1:10]*100)
pve <- 100*(GBC.pca.schaefer$sdev)^2/sum ((GBC.pca.schaefer$sdev)^2)
plot(pve, pch=16, 
   xlab="Principal Components",
  ylab="Prop. of variance explained")
```

#### PC1

```{r echo=FALSE}
pc1 <- as.data.frame(GBC.pca.schaefer$rotation[,1])
pc1$label <- row.names(pc1)
colnames(pc1) <- c("PC1","label")
ggseg(.data = pc1, atlas = "schaefer17_400", mapping=aes(fill=PC1), position = c("stacked")) + theme_void() + scale_fill_gradientn(colors = viridis_pal(option="B")(10))
```

Correlation with mean map 
```{r echo=FALSE}
means.tmp <- na.omit(GBC.schaefer.map)
cor.test(means.tmp$GBC.schaefer.map, pc1$PC1, method=c("spearman"))
```

#### Logistic Regression 

```{r}
GBC.pca.schaefer.scores <- as.data.frame(GBC.pca.schaefer$x[,1:10])
GBC.pca.schaefer.scores$subid <- participants$V1 
GBC.pca.schaefer.scores$sesid <- participants$V2
GBC.pca.schaefer.scores$drug <- participants$V3 
GBC.pca.schaefer.scores$meanFD <- participants$V4

summary(glm(as.factor(GBC.pca.schaefer.scores$drug) ~ GBC.pca.schaefer.scores$PC1 + GBC.pca.schaefer.scores$meanFD, family=binomial(logit)))
```

### Glasser 

**REHO PCA and PC scores logistic regression for drug/placebo prediction (Glasser)**

#### PCA Variance Explained

```{r}
inputmatrix <- GBC.glasser
inputmatrix <- inputmatrix %>% dplyr::select(-subid, -sesid, -drug, -meanFD) 
inputmatrix <- inputmatrix %>% mutate_if(is.character,as.numeric)
inputmatrix <- as.data.frame(inputmatrix) #convert matrix to df
inputmatrix[inputmatrix == 0] <- NA
inputmatrix.cleaned <- inputmatrix[, unlist(lapply(inputmatrix, function(x) !all(is.na(x))))] #remove all columns (parcels) with null data (all NAs) #84x232
GBC.pca.glasser <- prcomp(inputmatrix.cleaned, scale. = TRUE, center = TRUE) 
print(summary(GBC.pca.glasser)$importance[2,1:10]*100)
pve <- 100*(GBC.pca.glasser$sdev)^2/sum ((GBC.pca.glasser$sdev)^2)
plot(pve, pch=16, 
   xlab="Principal Components",
  ylab="Prop. of variance explained")
```

#### Logistic Regression 

```{r}
GBC.pca.glasser.scores <- as.data.frame(GBC.pca.glasser$x[,1:10])
GBC.pca.glasser.scores$subid <- participants$V1 
GBC.pca.glasser.scores$sesid <- participants$V2
GBC.pca.glasser.scores$drug <- participants$V3 
GBC.pca.glasser.scores$meanFD <- participants$V4 #match subids to scores

summary(glm(as.factor(GBC.pca.glasser.scores$drug) ~ GBC.pca.glasser.scores$PC1 + GBC.pca.glasser.scores$meanFD, family=binomial(logit)))
```

## SVM

```{r}
SVM_2class <- function(df,folds,feature_selection = F,feature_proportion = .1,num_repetitions = 100){
  #SVM 2-class classifier
  # folds: number of folds for cv.
  # feature_selection: optional flag for data-driven feature selection. Selects the proportion of features indicated by feature_proportion. Not used by default.
  # num_repetitions: How many times to you want to repeat the cv process using different random splits of the data. This is just extra caution against a randomly good or bad split.
  
  cat('\nRunning SVM models.....')
  # Set up folds for CV
  if (folds == "LOO") {
    # This is for leave-one-out cross-validation
    num_folds = length(unique(df$subid))
    num_repetitions <- 1
  } else {
    num_folds = folds
    num_repetitions <- num_repetitions
  }

  svm_output <- vector(mode = "list",length = num_repetitions) #set up output object.
  
  # Create the folds
  unique_IDs <- unique(df$subid)
  subid_folds <- replicate(num_repetitions,sample(unique_IDs,size = length(unique_IDs))) # create sets of random draws.
  foldIdxs <- data.frame(subid=unique_IDs)
  foldIdxs$foldID <- row_number(foldIdxs$subid)
  foldIdxs$foldID <- ntile(foldIdxs$foldID,num_folds)
  # cat('Sending data to CV')
  for (r in 1:num_repetitions) {
    foldIdxs$subid <- subid_folds[,r] # Grab a random split for folds.
    fold_output<-vector(mode = "list",length = num_folds)
    cat(sprintf('\nrepetition  %d.... ',r))
    for (fold in 1:num_folds) {
      # cat(sprintf('\nfold  %d.... ',fold))
      trainingIDs <- as.matrix(foldIdxs %>% filter(foldID != fold) %>% select(subid))
      trainingIndex <- df$subid %in% trainingIDs # indices for training subs
      trainingData <- df[trainingIndex, 3:dim(df)[2] ] %>% arrange(drug) #this is important because libsvm automatically makes the first observation class 1, so drug must be first every time. Placebo will be class -1.
      testData <- df[!trainingIndex, 4:dim(df)[2]] # test data. Take columns 4:end (Removes subid sesid drug).
      testLabels <- data.frame(df[!trainingIndex,c(1:3) ])
      # svm
      x <- as.matrix(trainingData[, 2:dim(trainingData)[2]])
      y <- as.factor(as.matrix(trainingData[,1]))
      svm.model <- svm(x =x, y = y, cost = 1, kernel = "linear",type = "C-classification",scale = F)
      svm.pred <- predict(svm.model, as.matrix(testData))
      
      w <- t(svm.model$coefs) %*% svm.model$SV #calculate feature weights.
      # num_features <- dim(x)[2]
      decisionValues <- w %*% t(testData)-svm.model$rho # Get decision valus.
      distance <- decisionValues/norm(w) #calculate distance from the classification hyperplane
      # just adding the results to the dataframe.
      testLabels$decisionValues <- t(decisionValues)
      testLabels$distance <- t(distance)
      testLabels$model.pred = svm.pred
      fold_output[[fold]]<-testLabels
    }
    svm_output[[r]] <- data.table::rbindlist(fold_output) # saving output for the repetition.
    cat('complete\n')
  }
  # output_list <- apply(subid_folds,CV_function,df=df,num_folds = num_folds,MARGIN = 2)
  
  # Now train a model using all the data. This is for the estimation of the feature weights using the most possible data.
  final_data<-df[, 3:dim(df)[2] ]
  x <- as.matrix(final_data[, 2:dim(final_data)[2]])
  y <- as.factor(as.matrix(final_data[,1]))
  svm.model <- svm(x = x, y = y, 
                   cost = 1, kernel = "linear",type = "C-classification",scale = F)
  w <- t(svm.model$coefs) %*% svm.model$SV
  svm_results <- list(svm_output,w,svm.model)
  cat('\nFinished SVM models\n')
  
  return(svm_results)
}
```

```{r}
AUC <- function(DecisionValues, labels){
  # This function creates an ROC curve and then calculates AUC.
  # Decision values is nx1
  # Labels is nx1
  
  # N.B.
  # Drug (class 0) is assigned as +1 by libsvm and placebo (class 1) is assigned as 0 by libsvm default. 
  # Adjust the true labels and predicted labels to match that here so that the decision values make sense.
  labels <- labels*-1+1
  
  P <- sum(labels == 1)
  N <- sum(labels == 0)
  Sorted_DecisionValues <- sort(unique(DecisionValues), decreasing = FALSE)
  numDecisionValues <- length(Sorted_DecisionValues)
  
  TP_Array <- vector(mode = "numeric",length = numDecisionValues)
  FP_Array <- vector(mode = "numeric",length = numDecisionValues)
  Accuracy_Array = vector(mode = "numeric",length = numDecisionValues)
  for (i in 1:numDecisionValues){
    thisCutoff <- Sorted_DecisionValues[i]
    thisPredictedLabels <- as.numeric(DecisionValues>thisCutoff)
    detections <- thisPredictedLabels==1
    
    TP <- sum(labels[detections] == thisPredictedLabels[detections])
    TPR <- TP/P
    FP <- sum(labels[detections]!=thisPredictedLabels[detections])
    FPR <- FP/N
    
    TP_Array[i] <- TPR
    FP_Array[i] <- FPR
    
    Accuracy_Array[i] = (TP + N - FP) / (P + N)
  }
  
  ROC_output <- data.frame(TPR =TP_Array,FPR=FP_Array,Accuracy = Accuracy_Array)
  ROC_output <- ROC_output%>%arrange(TPR,FPR)
  
  #AUC
  dFPR <- c(0,diff(ROC_output$FPR))
  dTPR <- c(0,diff(ROC_output$TPR))
  AUC <- sum(ROC_output$TPR * dFPR) + sum(dTPR * dFPR)/2
  return(AUC)
}
```

### Schaefer

```{r}
regionheaders <- schaefer.parcel.labels$label
demoheaders <- c("subid","sesid","drug","meanFD")
colheaders <- as.matrix(c(demoheaders,regionheaders))

df <- GBC.schaefer
colnames(df) <- colheaders
df <- df %>% select(-meanFD)
df <- df[, unlist(lapply(df, function(x) !all(is.na(x))))]
```

```{r, echo=T, eval=F}
model_results <- SVM_2class(df, "LOO")
saveRDS(model_results, file="/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.modelresults.schaefer.rds")
```
```{r}
model_results <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.modelresults.schaefer.rds")
prediction_output <- model_results[[1]]
```

```{r}
W<-model_results[[2]]
svm.model <- model_results[[3]]
num_features <- sum(!is.na(W[1,]))
```

#### Model accuracy
```{r}
accuracy_fun <- function(x) sum(x$model.pred==x$drug)/dim(x)[1] 
accuracies <- sapply(prediction_output,accuracy_fun) 
accuracy <- mean(accuracies)
accuracy
```

#### Number of correct classifications 

```{r}
num_obs <- length(prediction_output[[1]]$model.pred)
num_correct <- round(accuracy*num_obs)
num_correct
```

#### Permutation-based significance

```{r, echo=F,  eval = F, results='hide'}
num_permutations = 1000
nw=1
folds="LOO"

b <- binom.test(num_correct,num_obs,.5) #This is a binomial test. The p-value is not used (permutation test is used instead), but this function summarizes the data nicely.
b
b$pred_data <- prediction_output
b$accuracy <- accuracy

perm_acc <- matrix(nrow = num_permutations)
perm_W <- matrix(nrow = num_permutations,ncol = num_features)
perm_list <- list()

perm_list = foreach(perm_chunk = idiv(num_permutations,chunks = nw),
                        .combine=c,
                        .export = c("featureExtraction","SVM_2class"),
                        .packages = c("dplyr","e1071","matrixTests")) %do% {  # This must be `dopar` to be parallel.
                          perm_result_list=list()
                          for (p in 1:perm_chunk){
                            # thisPerm <- perms[p,]
                            cat(sprintf("\nPermutation %d",p))
                            thisDF <- df
                            # thisDF$drug <- df$drug[thisPerm]
                            permuted <- df %>% select(subid,drug) %>% group_by(subid) %>% mutate(perm_drug=sample(drug))
                            thisDF$drug <- permuted$perm_drug
                            perm_pred_result <- SVM_2class(thisDF,folds,
                                                           feature_selection = feature_selection,
                                                           feature_proportion = feature_proportion,
                                                           num_repetitions = 1)
                        
                            perm_result_list[[p]] = list(perm_pred_result)
                          }
                          perm_result_list
                        }

  #organizing the output
pred_data_list <- lapply(perm_list, function(x) x[[1]][[1]])
perm_Ws <- lapply(perm_list,function(x) x[[1]][[2]])
```


```{r, echo=T, eval=F}
# Calculating permutation accuracies and AUCs
perm_acc_distribution <- sapply(pred_data_list, function(x) sum(x[[1]]$model.pred==x[[1]]$drug)/length(x[[1]]$drug))

perm_p <- sum(perm_acc_distribution>accuracy)/length(perm_acc_distribution)

perm_auc_distribution <- sapply(pred_data_list, function(x) AUC(DecisionValues=x[[1]]$decisionValues,labels=x[[1]]$drug))
    
    
W_test <- sapply(perm_Ws, FUN = function(x) {
    abs(x)>abs(W)
    })
W_sig <- rowMeans(W_test)
    
b$perm_p <- perm_p
b$perm_W_sig <- W_sig
b$perm_accs = perm_acc_distribution
b$perm_aucs = perm_auc_distribution

  
saveRDS(b, file="/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.permutationresults.schaefer.rds")
```

```{r}
b <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.permutationresults.schaefer.rds")
```

```{r echo=FALSE}
cat(sprintf("The permuted accuracy is greater than the actual accuracy %s time", sum(b$perm_accs>accuracy)))

print(sprintf("Overall Accuracy: %1.3f; p = %.5f\n\n",accuracy,b$perm_p))
```

```{r echo=FALSE}
hist(b$perm_accs, col="#781d75", xlim = c(0.3, 0.7), main="", xlab="Accuracy")
abline(v = accuracy, col="#ffd000", lwd=4, lty=1)
```

#### Model weights map

```{r, warning=F, echo=F, comment=F, message=F}
SVM.weights.schaefer <- as.data.frame(t(W))
SVM.weights.schaefer$label <- row.names(SVM.weights.schaefer)

ggseg(.data = SVM.weights.schaefer, atlas = "schaefer17_400",  mapping=aes(fill=V1), position = c("stacked")) + theme_void() + scale_fill_gradient2(high= "goldenrod1", mid = "white", low = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL)
```

### Model weights S-A axis correlation

```{r echo=FALSE}
SAaxis.schaefer$label <- schaefer.parcel.labels$label
SVM.weights.schaefer.SA <- merge(SVM.weights.schaefer, SAaxis.schaefer, by="label")
cor.test(SVM.weights.schaefer.SA$V1, SVM.weights.schaefer.SA$finalrank.wholebrain, method=c("spearman"), exact=F)
```

### Model weights Inhibition correlation

```{r echo=FALSE}
mappys$label <- schaefer.parcel.labels$label
SVM.weights.schaefer.mappys <- merge(SVM.weights.schaefer, mappys, by="label")
cor.test(SVM.weights.schaefer.mappys$V1, SVM.weights.schaefer.mappys$PVALB, method=c("spearman"), exact=F)
```


### Glasser

```{r}
regionheaders <- glasser.parcel.labels$label
demoheaders <- c("subid","sesid","drug","meanFD")
colheaders <- as.matrix(c(demoheaders,regionheaders))

df <- GBC.glasser
colnames(df) <- colheaders
df <- df %>% select(-meanFD)
df <- df[, unlist(lapply(df, function(x) !all(is.na(x))))]
```

```{r, echo=T, eval=F}
model_results <- SVM_2class(df, "LOO")
saveRDS(model_results, file="/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.modelresults.glasser.rds")
```
```{r}
model_results <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.modelresults.glasser.rds")
prediction_output <- model_results[[1]]
```

```{r}
W<-model_results[[2]]
svm.model <- model_results[[3]]
num_features <- sum(!is.na(W[1,]))
```

#### Model accuracy
```{r}
accuracy_fun <- function(x) sum(x$model.pred==x$drug)/dim(x)[1] 
accuracies <- sapply(prediction_output,accuracy_fun) 
accuracy <- mean(accuracies)
accuracy
```

#### Number of correct classifications 

```{r}
num_obs <- length(prediction_output[[1]]$model.pred)
num_correct <- round(accuracy*num_obs)
num_correct
```

#### Permutation-based significance

```{r, echo=T,  eval = F, results='hide'}
num_permutations = 1000
nw=1
folds="LOO"

b <- binom.test(num_correct,num_obs,.5) #This is a binomial test. The p-value is not used (permutation test is used instead), but this function summarizes the data nicely.
b
b$pred_data <- prediction_output
b$accuracy <- accuracy

perm_acc <- matrix(nrow = num_permutations)
perm_W <- matrix(nrow = num_permutations,ncol = num_features)
perm_list <- list()

perm_list = foreach(perm_chunk = idiv(num_permutations,chunks = nw),
                        .combine=c,
                        .export = c("featureExtraction","SVM_2class"),
                        .packages = c("dplyr","e1071","matrixTests")) %do% {  # This must be `dopar` to be parallel.
                          perm_result_list=list()
                          for (p in 1:perm_chunk){
                            # thisPerm <- perms[p,]
                            cat(sprintf("\nPermutation %d",p))
                            thisDF <- df
                            # thisDF$drug <- df$drug[thisPerm]
                            permuted <- df %>% select(subid,drug) %>% group_by(subid) %>% mutate(perm_drug=sample(drug))
                            thisDF$drug <- permuted$perm_drug
                            perm_pred_result <- SVM_2class(thisDF,folds,
                                                           feature_selection = feature_selection,
                                                           feature_proportion = feature_proportion,
                                                           num_repetitions = 1)
                        
                            perm_result_list[[p]] = list(perm_pred_result)
                          }
                          perm_result_list
                        }

  #organizing the output
pred_data_list <- lapply(perm_list, function(x) x[[1]][[1]])
perm_Ws <- lapply(perm_list,function(x) x[[1]][[2]])
```


```{r, echo=T, eval=F}
# Calculating permutation accuracies and AUCs
perm_acc_distribution <- sapply(pred_data_list, function(x) sum(x[[1]]$model.pred==x[[1]]$drug)/length(x[[1]]$drug))

perm_p <- sum(perm_acc_distribution>accuracy)/length(perm_acc_distribution)

perm_auc_distribution <- sapply(pred_data_list, function(x) AUC(DecisionValues=x[[1]]$decisionValues,labels=x[[1]]$drug))
    
    
W_test <- sapply(perm_Ws, FUN = function(x) {
    abs(x)>abs(W)
    })
W_sig <- rowMeans(W_test)
    
b$perm_p <- perm_p
b$perm_W_sig <- W_sig
b$perm_accs = perm_acc_distribution
b$perm_aucs = perm_auc_distribution

  
saveRDS(b, file="/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.permutationresults.glasser.rds")
```

```{r}
b <- readRDS("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/GBC/GBC.SVM.permutationresults.glasser.rds")
```

```{r echo=FALSE}
cat(sprintf("The permuted accuracy is greater than the actual accuracy %s time", sum(b$perm_accs>accuracy)))

print(sprintf("Overall Accuracy: %1.3f; p = %.5f\n\n",accuracy,b$perm_p))
```

```{r echo=FALSE}
hist(b$perm_accs, col="#781d75", xlim = c(0.3, 0.7), main="", xlab="Accuracy")
abline(v = accuracy, col="#ffd000", lwd=4, lty=1)
```

#### Model weights map

```{r, warning=F, echo=F, comment=F, message=F}
SVM.weights.glasser <- as.data.frame(t(W))
SVM.weights.glasser$label <- row.names(SVM.weights.glasser)

ggseg(.data = SVM.weights.glasser, atlas = "glasser",  mapping=aes(fill=V1), position = c("stacked")) + theme_void() + scale_fill_gradient2(high= "goldenrod1", mid = "white", low = "#6f1282", guide = "colourbar", aesthetics = "fill", name = NULL)
```

### Model weights S-A axis correlation

```{r echo=FALSE}
SAaxis.glasser$label <- glasser.parcel.labels$label[181:360]
SVM.weights.glasser.SA <- merge(SVM.weights.glasser, SAaxis.glasser, by="label")
cor.test(SVM.weights.glasser.SA$V1, SVM.weights.glasser.SA$final.rank, method=c("spearman"), exact=F)
```
