---
title: "Alpraz Catch22 Group Maps: Visualize"
author: "Valerie Jill Sydnor"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
library(ciftiTools)
library(catch22)
library(rgl)
ciftiTools.setOption('wb_path', '/Users/valeriesydnor/Software/workbench/')
rgl::setupKnitr()
library(rmarkdown)
```

```{r}
xii.catch22.average.maps <- read_xifti("/cbica/projects/spatiotemp_dev_plasticity/Inhibition/Alpraz/catch22/catch22_average_maps.dscalar.nii")
xii.catch22.average.maps$data$cortex_left[xii.catch22.average.maps$data$cortex_left == 0] <- NA #convert 0 vertices to NA
xii.catch22.average.maps$data$cortex_right[xii.catch22.average.maps$data$cortex_right == 0] <- NA #convert 0 vertices to NA

surfL_fname <- read_surf("/Users/valeriesydnor/Software/workbench/workbench_files/Q1-Q6_R440.L.midthickness.32k_fs_LR.surf.gii")
surfR_fname <- read_surf("/Users/valeriesydnor/Software/workbench/workbench_files/Q1-Q6_R440.R.midthickness.32k_fs_LR.surf.gii")
xii.catch22.average.maps <- add_surf(xii.catch22.average.maps, surfL=surfL_fname, surfR=surfR_fname)
```

```{r}
mycolors <- c("#ffc229", "#ffd476", "#ffe3a8", "#fff3d8", "#fffffe", "#e4d1e6", "#bc90c2", "#9656a2", "#711784")
```

```{r}
visualize_maps <- function(measure, lower, upper){
  print("left hemisphere")
  print(summary(xii.catch22.average.maps$data$cortex_left[,measure]))
  hist(xii.catch22.average.maps$data$cortex_left[,measure])
  print("right hemisphere")
  print(summary(xii.catch22.average.maps$data$cortex_right[,measure]))      
  hist(xii.catch22.average.maps$data$cortex_right[,measure])
  view_xifti_surface(xii.catch22.average.maps, idx=measure, colors=c("inferno"), zlim=c(lower,upper), widget = TRUE)
}
```

**DN_HistogramMode_5**
```{r}
visualize_maps(1, -0.013, 0.013)
```

**DN_HistogramMode_10**
```{r}
visualize_maps(2, -0.018, 0.018)
```

**CO_f1ecac**
```{r}
visualize_maps(3, 1.99, 2.01)
```

**CO_FirstMin_ac**
```{r}
visualize_maps(4, 3.55, 4.2)
```

**CO_HistogramAMI_even_2_5**
```{r}
visualize_maps(5, 0.041, 0.045)
```

**CO_trev_1_num**
```{r}
visualize_maps(6, -0.015, 0.01)
```

**MD_hrv_classic_pnn40**
```{r}
visualize_maps(7, 0.959, 0.964)
```

**SB_BinaryStats_mean_longstretch1**
```{r}
visualize_maps(8, 9.25, 10.15)
```

**SB_TransitionMatrix_3ac_sumdiagcov**
```{r}
visualize_maps(9, 0.00345, 0.0042)
```

**PD_PeriodicityWang_th0_01**
```{r}
visualize_maps(10, 9.45, 11)
```

**CO_Embed2_Dist_tau_d_expfit_meandiff**
```{r}
visualize_maps(11, .175, .19)
```

**IN_AutoMutualInfoStats_40_gaussian_fmmi**
```{r}
visualize_maps(12, 1.05, 1.25)
```
**FC_LocalSimple_mean1_tauresrat**
```{r}
visualize_maps(13, 0.72, 0.85)
```

**DN_OutlierInclude_p_001_mdrmd**
```{r}
visualize_maps(14, 0.02, 0.06)
```

**DN_OutlierInclude_n_001_mdrmd**
```{r}
visualize_maps(15, 0.02, 0.075)
```

**SP_Summaries_welch_rect_area_5_1**
```{r}
visualize_maps(16, 0.33, 0.41)
```
**SB_BinaryStats_diff_longstretch0**
```{r}
visualize_maps(17, 6.75, 7.2)
```

**SB_MotifThree_quantile_hh**
```{r}
visualize_maps(18, 2.01, 2.05)
```

**SC_FluctAnal_2_rsrangefit_50_1_logi_prop_r1**
```{r}
visualize_maps(19, 0.231, 0.25)
```

**SC_FluctAnal_2_dfa_50_1_2_logi_prop_r1**
```{r}
visualize_maps(20, 0.22, 0.24)
```

**SP_Summaries_welch_rect_centroid**
```{r}
visualize_maps(21, 0.68, 0.77)
```

**FC_LocalSimple_mean3_stderr**
```{r}
visualize_maps(22, 1.135, 1.18)
```
